The pollination trade-off

### 2018-11-11 paper/manuscript.Rmd
Spellcheck to changes section

* Now using AICc instead of AIC to evaluate models (no change in results)
* Changes to traits: (*a*) to keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances. Also, now (*b*) columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits.
* The absolute/relative/gain terminology was confusing. Now  I'm modeling open and bagged pollen counts directly, using the bagged as a sort of control.
* Introduced visit efficacy instead of share in the pollen pool as a predictor in the model. Turns out to be a better predictor and also incorporates quantitative visitation data which was missing from the previous models. 
* Now I use a PCA of the explanatory variables to understand different plant strategies. 
* Introduction has been rewritten to be more *hypothesis* oriented. The manuscript also includes references thorughout.
* Added abstract

@@

* Spell-check everything
* Decide on a journal. Manuscript is currently written for an interdisciplinary one.

@@

* __Traits__: Currently I don't mention much traits in the discussion. I think the trait component is valuable and interesting but sadly at the moment the data quality is poor. Only 4 traits have been compiled: growth form, longevity, flower colour, and whether the plant is native to the region. It won't be possible to gather all of the traits used by @coux_linking_2016 from the literature but hopefully it is for a good proportion of them. Daniel and Jason, could we discuss options here?

>>>>

* Now using AICc instead of AIC to evaluate models (no change in results)
* Changes to traits: (*a*) to keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances. Also, now (*b*) columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits.
* The absolute/relative/gain terminology was confusing. Now  I'm modelling open and bagged pollen counts directly, using the bagged as a sort of control.
* Introduced visit efficacy instead of the share in the pollen pool as a predictor in the model. Turns out to be a better predictor and also incorporates quantitative visitation data which was missing from the previous models. 
* Now I use a PCA of the explanatory variables to understand different plant strategies. 
* Introduction has been rewritten to be more *hypothesis* oriented. The manuscript also includes references throughout.
* Added abstract

@@

* Spell-check everything
* Decide on a journal. The manuscript is currently written for an interdisciplinary one. 
* Check reference list

@@

* __Traits__: Currently I don't mention traits in the discussion. I think the trait component is valuable and interesting but sadly at the moment, the data quality is poor. Only 4 traits have been compiled: growth form, longevity, flower colour, and whether the plant is native to the region. It won't be possible to gather all of the traits used by @coux_linking_2016 from the literature but hopefully, it is for a good proportion of them. Daniel and Jason, could we discuss options here?
